Functional vs. Object Oriented Programming: Productivity comparison

### 2015-10-23 article.tex
Newer version

A quantitative method is used for this project because the authors will gather data from many sources and they will report in the paper. Afterward, the analysis of the gathered data will be performed so that the initial hypothesis will be either accepted or rejected.

The approach used will be deductive because we started this research with our own hypothesis on the basis of existing theories, for instance, regarding the benefits of FP and the advantages that developers can gain in software production.

Afterward, when the data will be acquired, the authors will perform observation and analysis of the gotten results. From that, it will be possible to accept or reject the initial hypothesis.

@@

@@

>>>>

A quantitative method is used for this project because the authors have gathered data from many sources and they report in this paper. Afterward, the analysis of the gathered data is performed so that the initial hypothesis will be either accepted or rejected.

The approach used is deductive because we started this research with our own hypothesis on the basis of existing theories, for instance, regarding the benefits of FP and the advantages that developers can gain in software production.

Afterward, when the data has been acquired, the authors perform observation and analysis of the gotten results. From that, it will be possible to accept or reject the initial hypothesis.

@@

\subsection{Lines of Code}

@@

\subsection{Code Reuse}
